### 2019-09-23 reports/thesis/chapters/5_inference.tex
Minor revise
Use proofreader

Returning back to the example at the start of the chapter, the empirical null could be used on the histogram shown in Figure \ref{fig:inference_inferenceIntro_histogram}. The resulting empirical null distribution is shown in Figure \ref{fig:inference_inferenceSubsampleAll}. The critical boundary, adjusted using the empirical null, which correspond to the 5\% FDR level was found to be $z\leqslant\inputNumber{../figures/inference/inferenceSubsampleAll_nullCritical1.txt}$ and $\inputNumber{../figures/inference/inferenceSubsampleAll_nullCritical2.txt}\geqslant z$ to 2 decimal places. This would test all pixels as negative which is incorrect.

The problem was that the empirical distribution of all of the test statistics looked like it did not came from a Normal distribution. It appeared that the test statistics varied spatially, suggesting the empirical null varied spatially as well. To account for the spatially variability of the null parameters, one possible extension is to the empirical null is to spilt the $z$ image into a grid and conduct inference in each section separately. There are problems with this though. The first problem is that how the grid is overlaid can be arbitrary, for example the grid can be translated to produce different sections. Secondly, it is not clear how to combine the results from each section together \citep{efron2008simultaneous}.

@@

The parameter of choice is the kernel radius $r$. A $r$ too small will treat defects as the null and will not detect them. A $r$ too big can also cause problems as well. The empirical null filter assumes that the null parameters vary smoothly and slowly so that the null test statistics captured by the kernel is somewhat Normal. If $r$ is too big, the kernel will capture far away test statistics with a very different null distributions. If all of these test statistics are pulled together into a histogram, the null distribution may not look Normal at all which can cause problems when fitting a Normal null distribution. Furthermore, if $r\rightarrow \infty$, then this is just using the empirical null on all pixels.

$r$ controls the proportion of pixels which are null captured by the kernel, denoted as $\pi_0$. $r$ should be selected so that $\pi_0$ is of a sensible value, for example $>90\%$. In practice, the defects are unknown so various kernel radiuses should be tried out. The kernel radius should be much larger than the size of the defect.

There exist similar filters, for example the local normalisation filter \citep{sage2003teaching, sage2018local} uses a Gaussian filter to obtain $\widehat{\mu}_{0,x,y}$. $\widehat{\sigma}_{0,x,y}^2$ was obtained by applying another Gaussian filter on the $\left(z_{x,y}-\widehat{\mu}_{0,x,y}\right)^2$ image. The purpose of this filter was to normalise images with uneven illumination. The disadvantage of using this filter, for estimating the null parameters, is that it uses a Gaussian filter. This is a type of weighted mean which is not robust to non-null statistics. In addition, the two Gaussian filters can have different radiuses, it is not clear how to set them.

@@

The empirical null filter was implemented using open source software called \emph{ImageJ} \citep{abramoff2004image, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}, available on \emph{GitHub} \citep{imagej2018rank}. This class implemented filters, such as the mean filter and median filter, using a circular kernel, making this a suitable framework for the empirical null filter. Figure \ref{fig:inference_fijiGui} shows the graphical user interface of the empirical null filter in \emph{Fiji} \citep{schindelin2012fiji}, a distribution of \emph{ImageJ}.

@@

As a test, the empirical null filter with $r=\SI{5}{\pixel}$ was used on a \emph{ImageJ} sample image \texttt{bridge.gif}, as shown in Figure \ref{fig:inference_fijiBridgeFilter}. It is meaningless to use the empirical null filter on an image not for the purpose of the filter, however, it did verify that the filter worked on arbitrary images with some computational considerations. The empirical null images $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ could be of interest, in particular, the empirical null mean image could be interpreted as the result of a mode filter \citep{griffin2000mean}. Figure \ref{fig:inference_fijiMean} compares the empirical null mean with other averaging filters. The empirical null mean has an impasto effect and preserved edges which is similar to the result in \cite{griffin2000mean}. Dispersion filters such as the standard deviation filter can be used to detect edges. Figure \ref{fig:inference_fijiStd} compares the standard deviation filter with the empirical null standard deviation. The resulting images were similar but it was notable that the edges in the empirical null standard deviation were sharper, suggesting that the empirical null standard deviation is a more robust measure of dispersion compared to the standard deviation.

@@

When using the the empirical null filter in \emph{ImageJ}, the user is presented with a menu, as shown in Figure \ref{fig:inference_fijiGui}. The user can input the kernel radius, the filter then modifies the currently selected image $z_{x,y}$ to $t_{x,y}$ for all $x$ and $y$ using a circular kernel with the specified radius. The menu also has options for by-product images to be shown such as: the empirical null mean $\widehat{\mu}_{0,x,y}$, the empirical null standard deviation $\widehat{\sigma}_{0,x,y}$, the standard deviation filter, quartile filters. Advanced options are available to the user, for example, the number of initial values set the number of valid solutions to be found when using the Newton-Raphson method to find the mode of the density estimate. The user can also set the maximum number of steps and tolerance for the Newton-Raphson method. The bandwidth parameters for the kernel density estimate can also be adjusted here.

@@

When the kernel captures pixels outside the boundary of the image or ROI, \texttt{RankFilters} uses nearest pixel padding which fills in pixels outside the ROI with values to the nearest pixels. Figure \ref{fig:inference_padding_nearest} shows an example of nearest pixel padding on the top left corner of a rectangle ROI. This is not suitable for the empirical null filter as this will cause bias in the density estimation. The empirical null filter uses \texttt{NaN} padding which fills pixels outside the ROI with \texttt{NaN}. This indicate that these pixels are outside the ROI and are ignored. The number of non-\texttt{NaN} captured by the kernel was kept track for calculations such as the bandwidth.

@@

Line filtering was done from left to right. At the start on the far left, an initial value of the median over the pixels in the kernel was used. In addition, various initial values were randomly tried out until a requested number of valid solutions were found. For the following pixel to the right, the empirical null mean of the neighbouring left pixel was used as the initial value. This was chosen as it was assumed the empirical null mean would vary slowly and smoothly spatially.

When filtering arbitrary images such as \texttt{bridge.gif}, a few computational considerations were needed. \texttt{bridge.gif} is an 8-bit image so values were represented as integers. This opened up opportunities for the inter-quartile range and the standard deviation to be zero. This caused problems as this would set the bandwidth to zero. When the standard deviation is zero, it was set to $0.289$ which corresponds to the standard deviation of a uniform random variable. When the inter-quartile range is zero, the inter-quartile range was set to the standard deviation $\times 1.34$.

@@

An experiment was conducted to demonstrate the effects of the empirical null filter on a simulated $\SI{256}{\pixel}\times\SI{256}{\pixel}$ Gaussian image, where all the pixels have value distributed as standard Normal. The purpose is to simulate test statistics which are null and no positive results should be detected. The test statistics after filtering should preserve its original distribution, or at least close to it. The statistical moments before and after filtering should be the same and were investigated. Because the empirical null mean and empirical null standard deviation are random variables, the filtered pixels will never be Normal and any normality tests would be too strict for the purpose of this experiment.

@@

An example of a Gaussian image with/without contamination before/after filtering are shown in Figures \ref{fig:inference_allNullGaussianScript} and \ref{fig:inference_allNullPlaneScript}. In the contaminated example, the filter managed to estimate the null mean, picking up the gradient. This enabled the filtered image to look flat and removed the contamination. The $p$-values after filtering are shown in Figure \ref{fig:inference_allNull_pValues}. A quick inspection suggest that the filtered pixels appeared reasonably Normal for this particular example.

For a given kernel radius $r$, 100 different Gaussian images were filtered to investigate the within image mean, standard deviation and kurtosis of the filtered statistics. Various other filters for normalisation were used as well such as the MAD mode null filter, median IQR null filter and the mean variance null filter. They use different estimators to estimate the null parameters as their name suggest, Table \ref{table:inference_nullFilters} clarifies them.

@@

The results for the filtered images are shown in Figures \ref{fig:inference_AllNullGaussian_mean}, \ref{fig:inference_AllNullGaussian_var} and \ref{fig:inference_AllNullGaussian_kurtosis}. For the filtered \emph{contaminated} images, they are in Figures \ref{fig:inference_AllNullPlane_mean}, \ref{fig:inference_AllNullPlane_var} and \ref{fig:inference_AllNullPlane_kurtosis}. The filtered test statistic means did agree with zero as expected, showing that the filters centred the statistics when normalising. When using the empirical null filter, there was some negative bias with the standard deviation of the filtered test statistics. The negative bias comes from the positive bias when estimating the null standard deviation.

@@

The kurtosis in Figures \ref{fig:inference_AllNullGaussian_kurtosis} and \ref{fig:inference_AllNullPlane_kurtosis} showed that the empirical null filter caused the filtered statistics to have heavy tails, in particular, for small kernel radiuses. This could cause problems in hypotheses testing because heavy tails could be misinterpreted as contribution from non-null statistics. The source of the kurtosis inflation is from the estimation of the null standard deviation. This can be seen by comparing the empirical null filter with the MAD mode null filter because the only difference between the two filters is in the estimation of the null standard deviation.

@@

The empirical null filter aims to estimate the null distribution parameters from $Z_{x,y}$ in order to normalise it to form $T_{x,y}$. By normalising it, $T_{x,y}|H_{0,x,y}$ should be approximately standard Normal and hypotheses testing can be used to detect defects.

Various defects were investigated. Speckle defect with density $\pi_1$ assign all test statistics to be non-null with probability $\pi_1$, and are null otherwise. This was chosen because the proportion of null statistics captured by the kernel should be the same for all kernel radiuses. A line defect assign columns of pixels to be non-null, a kernel would only capture a section of defect. A square defect was also investigated and a kernel can only capture the entire defect if its radius is large enough.

@@

An example of a speckle defected image is shown in Figure \ref{fig:inference_defectDustExample}, the figure also shows the image contaminated and then filtered. Without filtering, the top-left and bottom-right of the contaminated image have large, in magnitude, test statistics. In these areas, a lot of pixels would be tested as falsely positive. By using the empirical null filter, the resulting filtered image reassemble the uncontaminated image and appropriate inference can be done on the filtered image. However, some statistical power was lost when conducting hypotheses testing on the filtered image because in areas of high empirical null standard deviation, the normalised statistics became too small which then decreased the detection power. This cannot be avoided as areas of high empirical null standard deviation was due to the randomness in sampling. Similar comments can be made for the line defect as shown in Figure \ref{fig:inference_defectLineExample}.

@@

The empirical null mean in Figure \ref{fig:inference_defectSquareExample} demonstrated the multi-thread nature of the implementation of the empirical null filter. It can be seen that there were horizontal streaks where the defect is. This is the result of each thread filtering a row and jumping from one mode, the null, to the other, the non-null, at different times. The horizontal streaks can be removed by using more initial values so that the Newton-Raphson method can pin point which mode is greater.

Figure \ref{fig:inference_defectExamplePValue} shows the $p$-values after filtering a contaminated defected image. The FDR can be estimated in these figures by dividing the number of null statistics in the critical region by the number of statistics in the critical region. With a sensible kernel radius, some of the defects can be detected. False negatives are common but this is inevitable in order to control for the FDR. The figure shows that using a kernel radius of $r=\SI{20}{\pixel}$, for the square defect, tested no pixels for defects. This, again, emphasise the importance of a good kernel radius.

@@

The ROC curves considers all thresholds or specificities used in the hypotheses testing. In the previous experiment, it was found variance of the test statistics were different before and after filtering. As a result, for a given threshold, such as the 5\% FDR level, the specificity may change ever so slightly after filtering.

@@

The results are shown in Figure \ref{fig:inference_DefectSimulationDust}. The AUC quantified showed that using the filter improved the performance of the test from the contamination. The type 1 error, or specificity, did decreased after filtering. However, the results illustrated that the FDR is controlled quite well at around 5\% after filtering. This meant that in this particular example, the FDR control is consistent after filtering. At situations with low detection power, the FDR can fluctuate between 0 and 1 and can take only so many values. For example if 3 positive pixels were detected, then the FDR can only take values of multiples of $1/3$ between and including 0 and 1.

@@

There is the question of what kernel radius to choose for a given defect. Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $\pi_1=0.1$ to satisfy some assumptions made for the empirical null. Given the size of the defect, one could work out the minimum kernel radius by setting a threshold for the maximum proportion of the area of kernel which contains a defect to 10\%. In other words, for a kernel with radius $r$
\begin{equation}
0.1 > \dfrac{\text{maximum area of defect captured by the kernel}}{\text{area of kernel}} \ .
\end{equation}
For a $d \times d$ square defect, this is $r > d \sqrt{10/\pi}$.
In the example of $d=\SI{30}{\pixel}$, this is about $r>\SI{54}{\pixel}$. For the line defect with thickness $\SI{5}{\pixel}$, the radius is about $r>\SI{32}{\pixel}$. These are rules of thumb because the kernel is not perfectly circular when used on a grid of pixels. It should be pointed out that the implementation can accept non-integer radiuses if desired.

@@

An experiment was conducted where the contaminated defected image were filtered using various kernel radiuses for a fixed alternative distribution $\normal(3,1)$. Hypotheses testing was done on the uncontaminated and filtered contaminated image. The AUC and various errors were recorded, this was repeated 100 times. The AUC was obtained by numerically integrating the ROC curve using the trapezium rule with 1\,000 trapeziums. The results of the uncontaminated image were all pooled together to obtain the empirical distribution of the AUC and errors without contamination. Results for the line and square defect are shown in Figures \ref{fig:inference_Experiment_DefectRadiusLine} and \ref{fig:inference_Experiment_DefectRadiusSquare} respectively.

The results showed that the AUC increased with kernel radius. This highlighted that a kernel with a good radius can perform almost as though there was no contamination. It also appeared that the optimal AUC was achieved when using the kernel radius from the rule of thumb, making these results consistent with literature.

@@

\afterpage{\clearpage}
\section{Results}

@@

The false positives were tackled by manually segmenting the image further as shown in Figure \ref{fig:inference_segmentFurther}. It was segmented using the edges of the $z$ image. The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on. The resulting filtered segments were stitched together to form the resulting filtered image. By using this method, the resulting inference is shown in Figure \ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}. It can be seen that the empirical null mean did change face to face, resulting in a clear boundary set by the edges. Most of false positives around the corners and edges have been eliminated.

@@

The empirical null filter demonstrated that it can adjust the null hypotheses according to the data to make sensible inference. In the simulations, it was found that the FDR level is preserved after filtering. Also, the empirical null filter outperformed other methods based on quantiles, as suggested by \cite{efron2004large}. A sensible kernel radius is required to aid distinguishing misspecified null statistics from non-null statistics, for example, a kernel too small would treat defects as the null.

@@

There are a few strategies to accelerate the filter. The empirical null filter may be accelerated using GPUs \citep{yang2008parallel, hwu2011gpu, eklund2013medical}, however, efforts to implement the filter in \emph{CUDA} and \emph{C++} is fruitless if there may exist a faster method. Instead, accuracy may be sacrificed for speed by only estimating the null parameters for a number of regularly spaced pixels, the remaining pixels are interpolated. This requires the null parameters to be slowly varying, otherwise, the interpolation may underfit. This may cause problems because of the face to face transition observed in the experiments. It was found that if a bad solution was found for a point, then that solution would spread its bad solution to neighbouring pixels due to the interpolation.

Estimation of the null parameters is essentially robust statistics, estimating the parameters of the null distribution without being affected by non-null statistics. Potential faster methods compared to the empirical null could exist in literature for robust statistics such as \cite{hampel1986robust, rousseeuw1987robust, maronna2006robust, huber2009robust, jewson2018principles}. The use of density estimation for robust estimation is also featured when using loss functions derived from the Hellinger-divergence \citep{beran1977minimum, jewson2018principles} or the beta-divergence \citep{basu1998robust, jewson2018principles} which bears similarities to the empirical null. However, numerical methods are still required to find the mode. Exact estimation of the mode using Bayesian methods is impossible \citep{heinrich2013the} which suggest avoiding the use of numerical methods can be difficult.

The EM algorithm \citep{dempster1977maximum} could be used to fit a mixture of Gaussians to identify the null distribution and estimate its parameters. However the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.

>>>>

Returning to the example at the start of the chapter, the empirical null could be used on the histogram shown in Figure \ref{fig:inference_inferenceIntro_histogram}. The resulting empirical null distribution is shown in Figure \ref{fig:inference_inferenceSubsampleAll}. The critical boundary, adjusted using the empirical null, which corresponds to the 5\% FDR level was found to be $z\leqslant\inputNumber{../figures/inference/inferenceSubsampleAll_nullCritical1.txt}$ and $\inputNumber{../figures/inference/inferenceSubsampleAll_nullCritical2.txt}\geqslant z$ to 2 decimal places. This would test all pixels as negative which is incorrect.

The problem was that the empirical distribution of all of the test statistics looked like it did not come from a Normal distribution. It appeared that the test statistics varied spatially, suggesting the empirical null varied spatially as well. To account for the spatial variability of the null parameters, one possible extension is to the empirical null is to spilt the $z$ image into a grid and conduct inference in each section separately. There are problems with this though. The first problem is that how the grid is overlaid can be arbitrary, for example, the grid can be translated to produce different sections. Secondly, it is not clear how to combine the results from each section together \citep{efron2008simultaneous}.

@@

The parameter of choice is the kernel radius $r$. A $r$ too small will treat defects as the null and will not detect them. A $r$ too big can also cause problems as well. The empirical null filter assumes that the null parameters vary smoothly and slowly so that the null test statistics captured by the kernel is somewhat Normal. If $r$ is too big, the kernel will capture distanced test statistics with very different null distributions. If all of these test statistics are pulled together into a histogram, the null distribution may not look Normal at all which can cause problems when fitting a Normal null distribution. Furthermore, if $r\rightarrow \infty$, then this is just using the empirical null on all pixels.

$r$ controls the proportion of pixels which are null captured by the kernel, denoted as $\pi_0$. $r$ should be selected so that $\pi_0$ is of sensible value, for example, $>90\%$. In practice, the defects are unknown so various kernel radiuses should be tried out. The kernel radius should be much larger than the size of the defect.

There exist similar filters, for example the local normalisation filter \citep{sage2003teaching, sage2018local} uses a Gaussian filter to obtain $\widehat{\mu}_{0,x,y}$. $\widehat{\sigma}_{0,x,y}^2$ was obtained by applying another Gaussian filter on the $\left(z_{x,y}-\widehat{\mu}_{0,x,y}\right)^2$ image. The purpose of this filter was to normalise images with uneven illumination. The disadvantage of using this filter, for estimating the null parameters, is that it uses a Gaussian filter. This is a type of weighted mean which is not robust to non-null statistics. Also, the two Gaussian filters can have different radiuses, it is not clear how to set them.

@@

The empirical null filter was implemented using open-source software called \emph{ImageJ} \citep{abramoff2004image, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}, available on \emph{GitHub} \citep{imagej2018rank}. This class implemented filters, such as the mean filter and median filter, using a circular kernel, making this a suitable framework for the empirical null filter. Figure \ref{fig:inference_fijiGui} shows the graphical user interface of the empirical null filter in \emph{Fiji} \citep{schindelin2012fiji}, a distribution of \emph{ImageJ}.

@@

As a test, the empirical null filter with $r=\SI{5}{\pixel}$ was used on a \emph{ImageJ} sample image \texttt{bridge.gif}, as shown in Figure \ref{fig:inference_fijiBridgeFilter}. It is meaningless to use the empirical null filter on an arbitrary image, however, it did verify that the filter coped with it with some computational considerations. The empirical null images $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ could be of interest, in particular, the empirical null mean image could be interpreted as the result of a mode filter \citep{griffin2000mean}. Figure \ref{fig:inference_fijiMean} compares the empirical null mean with other averaging filters. The empirical null mean has an impasto effect and preserved edges which are similar to the result in \cite{griffin2000mean}. Dispersion filters such as the standard deviation filter can be used to detect edges. Figure \ref{fig:inference_fijiStd} compares the standard deviation filter with the empirical null standard deviation. The resulting images were similar but it was notable that the edges in the empirical null standard deviation were sharper, suggesting that the empirical null standard deviation is a more robust measure of dispersion compared to the standard deviation.

@@

When using the empirical null filter in \emph{ImageJ}, the user is presented with a menu, as shown in Figure \ref{fig:inference_fijiGui}. The user can input the kernel radius, the filter then modifies the currently selected image $z_{x,y}$ to $t_{x,y}$ for all $x$ and $y$ using a circular kernel with the specified radius. The menu also has options for by-product images to be shown: the empirical null mean $\widehat{\mu}_{0,x,y}$, the empirical null standard deviation $\widehat{\sigma}_{0,x,y}$, the standard deviation filter, quartile filters. Advanced options are available to the user, for example, the number of initial values set the number of valid solutions to be found when using the Newton-Raphson method to find the mode of the density estimate. The user can also set the maximum number of steps and tolerance for the Newton-Raphson method. The bandwidth parameters for the kernel density estimate can also be adjusted here.

@@

When the kernel captures pixels outside the boundary of the image or ROI, \texttt{RankFilters} uses nearest pixel padding which fills in pixels outside the ROI with values to the nearest pixels. Figure \ref{fig:inference_padding_nearest} shows an example of nearest pixel padding on the top left corner of a rectangle ROI. This is not suitable for the empirical null filter as this will cause bias in the density estimation. The empirical null filter uses \texttt{NaN} padding which fills pixels outside the ROI with \texttt{NaN}. This indicates that these pixels are outside the ROI and are ignored. The number of non-\texttt{NaN} captured by the kernel was kept track for calculations such as the bandwidth.

@@

Line filtering was done from left to right. At the start on the far left, an initial value of the median over the pixels in the kernel was used. Also, various initial values were randomly tried out until a requested number of valid solutions were found. For the following pixel to the right, the empirical null mean of the neighbouring left pixel was used as the initial value. This was chosen as it was assumed the empirical null mean would vary slowly and smoothly spatially.

When filtering arbitrary images such as \texttt{bridge.gif}, a few computational considerations were needed. \texttt{bridge.gif} is an 8-bit image so values were represented as integers. This opened up opportunities for the interquartile range and the standard deviation to be zero. This caused problems as this would set the bandwidth to zero. When the standard deviation is zero, it was set to $0.289$ which corresponds to the standard deviation of a uniform random variable. When the inter-quartile range is zero, the inter-quartile range was set to the standard deviation $\times 1.34$.

@@

An experiment was conducted to demonstrate the effects of the empirical null filter on a simulated $\SI{256}{\pixel}\times\SI{256}{\pixel}$ Gaussian image, where all the pixels have value distributed as standard Normal. The purpose is to simulate test statistics which are null and no positive results should be detected. The test statistics after filtering should preserve its original distribution, or at least close to it. The statistical moments before and after filtering should be the same and were investigated. Because the empirical null mean and empirical null standard deviation are random variables, the filtered pixels will never be Normal and any normality tests would be too strict for this experiment.

@@

An example of a Gaussian image with/without contamination before/after filtering are shown in Figures \ref{fig:inference_allNullGaussianScript} and \ref{fig:inference_allNullPlaneScript}. In the contaminated example, the filter managed to estimate the null mean, picking up the gradient. This enabled the filtered image to look flat and removed the contamination. The $p$-values after filtering are shown in Figure \ref{fig:inference_allNull_pValues}. A quick inspection suggests that the filtered pixels appeared reasonably Normal for this particular example.

For a given kernel radius $r$, 100 different Gaussian images were filtered to investigate the within image mean, standard deviation and kurtosis of the filtered statistics. Various other filters for normalisation were used as well such as the MAD mode null filter, median IQR null filter and the mean variance null filter. They use different estimators to estimate the null parameters as their name suggests, Table \ref{table:inference_nullFilters} clarifies them.

@@

The results for the filtered images are shown in Figures \ref{fig:inference_AllNullGaussian_mean}, \ref{fig:inference_AllNullGaussian_var} and \ref{fig:inference_AllNullGaussian_kurtosis}. For the filtered \emph{contaminated} images, they are in Figures \ref{fig:inference_AllNullPlane_mean}, \ref{fig:inference_AllNullPlane_var} and \ref{fig:inference_AllNullPlane_kurtosis}. The filtered test statistic means did agree with zero as expected, showing that the filters centred the statistics when normalising. When using the empirical null filter, there was some negative bias with the standard deviation of the filtered test statistics. The negative bias comes from a positive bias when estimating the null standard deviation.

@@

The kurtosis in Figures \ref{fig:inference_AllNullGaussian_kurtosis} and \ref{fig:inference_AllNullPlane_kurtosis} showed that the empirical null filter caused the filtered statistics to have heavy tails, in particular, for small kernel radiuses. This could cause problems in hypotheses testing because heavy tails could be misinterpreted as a contribution from non-null statistics. The source of the kurtosis inflation is from the estimation of the null standard deviation. This can be seen by comparing the empirical null filter with the MAD mode null filter because the only difference between the two filters is in the estimation of the null standard deviation.

@@

The empirical null filter aims to estimate the null distribution parameters from $Z_{x,y}$ to normalise it to form $T_{x,y}$. By normalising it, $T_{x,y}|H_{0,x,y}$ should be approximately standard Normal and hypotheses testing can be used to detect defects.

Various defects were investigated. Speckle defect with density $\pi_1$ assign all test statistics to be non-null with probability $\pi_1$ and are null otherwise. This was chosen because the proportion of null statistics captured by the kernel should be the same for all kernel radiuses. A line defect assigns columns of pixels to be non-null, a kernel would only capture a section of the defect. A square defect was also investigated and a kernel can only capture the entire defect if its radius is large enough.

@@

An example of a speckle defected image is shown in Figure \ref{fig:inference_defectDustExample}, the figure also shows the image contaminated and then filtered. Without filtering, the top-left and bottom-right of the contaminated image have large, in magnitude, test statistics. In these areas, a lot of pixels would be tested as falsely positive. By using the empirical null filter, the resulting filtered image reassemble the uncontaminated image and appropriate inference can be done on the filtered image. However, some statistical power was lost when conducting hypotheses testing on the filtered image because, in areas of high empirical null standard deviation, the normalised statistics became too small which then decreased the detection power. This cannot be avoided as areas of high empirical null standard deviation was due to the randomness in sampling. Similar comments can be made for the line defect as shown in Figure \ref{fig:inference_defectLineExample}.

@@

The empirical null mean in Figure \ref{fig:inference_defectSquareExample} demonstrated the multi-thread nature of the implementation of the empirical null filter. It can be seen that there were horizontal streaks where the defect is. This is the result of each thread filtering a row and jumping from one mode, the null, to the other, the non-null, at different times. The horizontal streaks can be removed by using more initial values so that the Newton-Raphson method can pinpoint which mode is greater.

Figure \ref{fig:inference_defectExamplePValue} shows the $p$-values after filtering a contaminated defected image. The FDR can be estimated in these figures by dividing the number of null statistics in the critical region by the number of statistics in the critical region. With a sensible kernel radius, some of the defects can be detected. False negatives are common but this is inevitable to control for the FDR. The figure shows that using a kernel radius of $r=\SI{20}{\pixel}$, for the square defect, tested no pixels for defects. This, again, emphasise the importance of a good kernel radius.

@@

The ROC curves consider all thresholds or specificities used in the hypotheses testing. In the previous experiment, it was found the variance of the test statistics were different before and after filtering. As a result, for a given threshold, such as the 5\% FDR level, the specificity may change ever so slightly after filtering.

@@

The results are shown in Figure \ref{fig:inference_DefectSimulationDust}. The AUC quantified showed that using the filter improved the performance of the test from the contamination. The type 1 error, or specificity, did decrease after filtering. However, the results illustrated that the FDR is controlled quite well at around 5\% after filtering. This meant that in this particular example, FDR control is consistent after filtering. At situations with low detection power, the FDR can fluctuate between 0 and 1 and can take only so many values. For example, if 3 positive pixels were detected, then the FDR can only take values of multiples of $1/3$ between and including 0 and 1.

@@

There is the question of what kernel radius to choose for a given defect. Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $\pi_1=0.1$ to satisfy some assumptions made for the empirical null. Given the size of the defect, one could work out the minimum kernel radius by setting a threshold for the maximum proportion of the area of the kernel which contains a defect to 10\%. In other words, for a kernel with radius $r$
\begin{equation}
0.1 > \dfrac{\text{maximum area of defect captured by the kernel}}{\text{area of kernel}} \ .
\end{equation}
For a $d \times d$ square defect, this is $r > d \sqrt{10/\pi}$.
In the example of $d=\SI{30}{\pixel}$, this is about $r>\SI{54}{\pixel}$. For the line defect with thickness $\SI{5}{\pixel}$, the radius is about $r>\SI{32}{\pixel}$. These are rules of thumb because the kernel is not perfectly circular when used on a grid of pixels. It should be pointed out that the implementation can accept non-integer radiuses if desired.

@@

An experiment was conducted where the contaminated defected image was filtered using various kernel radiuses for a fixed alternative distribution $\normal(3,1)$. Hypotheses testing was done on the uncontaminated and filtered contaminated image. The AUC and various errors were recorded, this was repeated 100 times. The AUC was obtained by numerically integrating the ROC curve using the trapezium rule with 1\,000 trapeziums. The results of the uncontaminated image were all pooled together to obtain the empirical distribution of the AUC and errors without contamination. Results for the line and square defect are shown in Figures \ref{fig:inference_Experiment_DefectRadiusLine} and \ref{fig:inference_Experiment_DefectRadiusSquare} respectively.

The results showed that the AUC increased with kernel radius. This highlighted that a kernel with a good radius can perform almost as though there was no contamination. It also appeared that the optimal AUC was achieved when using the kernel radius from the rule of thumb, making these results consistent with the literature.

@@

\afterpage{\clearpage}
\subsection{Application to Real Projections}

@@

The false positives were tackled by manually segmenting the image further as shown in Figure \ref{fig:inference_segmentFurther}. It was segmented using the edges of the $z$ image. The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on. The resulting filtered segments were stitched together to form the resulting filtered image. By using this method, the resulting inference is shown in Figure \ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}. It can be seen that the empirical null mean did change face to face, resulting in a clear boundary set by the edges. Most of the false positives around the corners and edges have been eliminated.

@@

The empirical null filter demonstrated that it can adjust the null hypotheses according to the data to make a sensible inference. In the simulations, it was found that the FDR level is preserved after filtering. Also, the empirical null filter outperformed other methods based on quantiles, as suggested by \cite{efron2004large}. A sensible kernel radius is required to avoid treating defects as the null.

@@

There are a few strategies to accelerate the filter. The empirical null filter may be accelerated using GPUs \citep{yang2008parallel, hwu2011gpu, eklund2013medical}, however, efforts to implement the filter in \emph{CUDA} and \emph{C++} is fruitless if there may exist a faster method. Instead, accuracy may be sacrificed for speed by only estimating the null parameters for several regularly spaced pixels, the remaining pixels are interpolated. This requires the null parameters to be slowly varying, otherwise, the interpolation may underfit. This may cause problems because of the face to face transition observed in the experiments. It was found that if a bad solution was found for a point, then that solution would spread its bad solution to neighbouring pixels due to the interpolation.

Estimation of the null parameters is essentially robust statistics, estimating the parameters of the null distribution without being affected by non-null statistics. Potential faster methods compared to the empirical null could exist in the literature for robust statistics such as \cite{hampel1986robust, rousseeuw1987robust, maronna2006robust, huber2009robust, jewson2018principles}. The use of density estimation for robust estimation is also featured when using loss functions derived from the Hellinger-divergence \citep{beran1977minimum, jewson2018principles} or the beta-divergence \citep{basu1998robust, jewson2018principles} which bears similarities to the empirical null. However, numerical methods are still required to find the mode. Exact estimation of the mode using Bayesian methods is impossible \citep{heinrich2013the} which suggest avoiding the use of numerical methods can be difficult.

The EM algorithm \citep{dempster1977maximum} could be used to fit a mixture of Gaussians to identify the null distribution and estimate its parameters. However, the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.
